\textsf{Are large language models superhuman chemists?}

### 2024-03-30 src/tex/appendix.tex
update

\begin{table}
    \caption{\textbf{Spearman correlation coefficients for the correlation of model performance with molecular features.} The table shows the Spearman correlation}
    \begin{tabularx}{\textwidth}{XXXX XXXX}
        \toprule
        topic & molecular descriptor & \(\rho\) GPT-4 & \(\rho \) Claude 3 & \( \rho \) Galactica &  \( \rho \) humans  \\ 
        \midrule
        number of \gls{nmr} signals & number of atoms &  \variable{output/correlation_correlation/spearman_num_atoms_gpt4_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_num_atoms_claude3_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_num_atoms_galactica_120b_is_number_nmr_peaks.txt}  & \variable{output/correlation_correlation/spearman_num_atoms_human_is_number_nmr_peaks.txt} \\
                              & complexity & \variable{output/correlation_correlation/spearman_complexity_gpt4_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_complexity_claude3_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_complexity_galactica_120b_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_complexity_human_is_number_nmr_peaks.txt} \\
        \midrule 
        total electron counts & number of atoms & \variable{output/correlation_correlation/spearman_num_atoms_gpt4_is_electron_counts.txt} & \variable{output/correlation_correlation/spearman_num_atoms_claude3_is_electron_counts.txt} & \variable{output/correlation_correlation/spearman_num_atoms_galactica_120b_is_electron_counts.txt} & \variable{output/correlation_correlation/spearman_num_atoms_human_is_electron_counts.txt} \\
        \midrule 
        \gls{smiles} \gls{iupac} name matching & number of atoms & \variable{output/correlation_correlation/spearman_num_atoms_gpt4_is_name.txt} & \variable{output/correlation_correlation/spearman_num_atoms_claude3_is_name.txt} & \variable{output/correlation_correlation/spearman_num_atoms_galactica_120b_is_name.txt} & \variable{output/correlation_correlation/spearman_num_atoms_human_is_name.txt} \\
                & complexity & \variable{output/correlation_correlation/spearman_complexity_gpt4_is_name.txt} & \variable{output/correlation_correlation/spearman_complexity_claude3_is_name.txt} & \variable{output/correlation_correlation/spearman_complexity_galactica_120b_is_name.txt} & \variable{output/correlation_correlation/spearman_complexity_human_is_name.txt} \\
        \bottomrule
    \end{tabularx}
    \label{tab:correlation_coefficients}
\end{table}

>>>>

\begin{table}
    \caption{\textbf{Spearman correlation coefficients for the correlation of model performance with molecular features.} The table shows the Spearman correlation coefficient $\rho$ for the correlation of the performance of the models with the number of atoms and the complexity of the molecules. }
    \begin{tabularx}{\textwidth}{XXXX XXXX}
        \toprule
        topic & molecular descriptor & \(\rho\) GPT-4 & \(\rho \) Claude 3 & \( \rho \) Galactica &  \( \rho \) humans  \\ 
        \midrule
        number of \gls{nmr} signals & number of atoms &  \variable{output/correlation_correlation/spearman_num_atoms_gpt4_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_num_atoms_claude3_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_num_atoms_galactica_120b_is_number_nmr_peaks.txt}  & \variable{output/correlation_correlation/spearman_num_atoms_human_is_number_nmr_peaks.txt} \\
                              & complexity & \variable{output/correlation_correlation/spearman_complexity_gpt4_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_complexity_claude3_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_complexity_galactica_120b_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_complexity_human_is_number_nmr_peaks.txt} \\
        \midrule 
        total electron counts & number of atoms & \variable{output/correlation_correlation/spearman_num_atoms_gpt4_is_electron_counts.txt} & \variable{output/correlation_correlation/spearman_num_atoms_claude3_is_electron_counts.txt} & \variable{output/correlation_correlation/spearman_num_atoms_galactica_120b_is_electron_counts.txt} & \variable{output/correlation_correlation/spearman_num_atoms_human_is_electron_counts.txt} \\
        \midrule 
        \gls{smiles} \gls{iupac} name matching & number of atoms & \variable{output/correlation_correlation/spearman_num_atoms_gpt4_is_name.txt} & \variable{output/correlation_correlation/spearman_num_atoms_claude3_is_name.txt} & \variable{output/correlation_correlation/spearman_num_atoms_galactica_120b_is_name.txt} & \variable{output/correlation_correlation/spearman_num_atoms_human_is_name.txt} \\
                & complexity & \variable{output/correlation_correlation/spearman_complexity_gpt4_is_name.txt} & \variable{output/correlation_correlation/spearman_complexity_claude3_is_name.txt} & \variable{output/correlation_correlation/spearman_complexity_galactica_120b_is_name.txt} & \variable{output/correlation_correlation/spearman_complexity_human_is_name.txt} \\
        \bottomrule
    \end{tabularx}
    \label{tab:correlation_coefficients}
\end{table}
